### 2023-07-13 paper/sec-dis-pseudodata.tex
Start updaing plots

%-----------------------------------------------------------------------
\begin{figure}[t]
    \centering
\includegraphics[width=0.8\textwidth]{plots/Nevent_FASERv2_14.pdf}
\caption{\small The event yields per bin $N_{\rm ev}^{(i)}$,  Eq.~(\ref{eq:event_yields}),
  for muon neutrinos at the FASER$\nu$2 detector, restricted
  to the DIS region defined by Eq.~(\ref{eq:DISconditions}).
  %
  We present results binned in $x$ and $Q^2$ integrated over neutrino energies.
  %
  The red dots indicate the weighted bin center.
  %
  Adding up all the bins in this plot results into the $N_{\nu_\mu}$ value listed in
Table~\ref{tab:integrated_rates}.}
    \label{fig:fasernu2_muon}
\end{figure}
%-----------------------------------------------------------------------

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
    \centering
    \includegraphics[width = 0.8\textwidth]{plots/Kin_nNNPDF30_EIC_FPF.pdf}
    \caption{The kinematic coverage of FASER$\nu$2 in the $(x,Q^2)$ plane,
      same as  Fig.~\ref{fig:fasernu2_muon},
      compared to that of electron-ion collisions
      at the EIC for the highest center-of-mass energies $\sqrt{s}$ planned,
      as well as to the coverage of other available hard-scattering datasets involving
      nuclear targets or projectiles.
      %
      Specifically, we display the coverage of fixed-target neutral- and charged-current nuclear DIS,
      fixed-target Drell-Yan production, and $W$, $Z$, $D$-meson, photon, and dijet
      production in proton-lead collisions at the LHC.
      }
    \label{fig:Kin_nNNPDF30_EIC_FPF}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

%-----------------------------------------------------------------------
\begin{figure}[t]
    \centering
	\includegraphics[width=0.495\textwidth]{plots/FPF-FASERv.pdf}
	\includegraphics[width=0.495\textwidth]{plots/FPF-FASERv2.pdf}
	\includegraphics[width=0.495\textwidth]{plots/FPF-FLArE100.pdf}
	\includegraphics[width=0.495\textwidth]{plots/FPF-SND.pdf}
	\caption{\small The event yields per bin $N_{\rm ev}^{(i)}$, for muon neutrinos at the FASER$\nu$(2)
	and AdvSND detectors, and electron neutrinos the FLArE detector, restricted to the DIS region defined 
	by Eq.~(\ref{eq:DISconditions}).
	%
	Adding up all the bins in this plot results into the $N_{\nu_\mu}$ value listed in
	Table~\ref{tab:integrated_rates}.}
    \label{fig:fasernu2_muon}
\end{figure}
%-----------------------------------------------------------------------

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
    \centering
    \includegraphics[width = 0.9\textwidth]{plots/Kin_nNNPDF30_EIC_FPF.pdf}
    \caption{The kinematic coverage of FASER$\nu$2 in the $(x,Q^2)$ plane,
      same as  Fig.~\ref{fig:fasernu2_muon},
      compared to that of electron-ion collisions
      at the EIC for the highest center-of-mass energies $\sqrt{s}$ planned,
      as well as to the coverage of other available hard-scattering datasets involving
      nuclear targets or projectiles.
      %
      Specifically, we display the coverage of fixed-target neutral- and charged-current nuclear DIS,
      fixed-target Drell-Yan production, and $W$, $Z$, $D$-meson, photon, and dijet
      production in proton-lead collisions at the LHC.
      }
    \label{fig:Kin_nNNPDF30_EIC_FPF}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
